%---------------------------------------------------------------
\chapter{Literature review}
%---------------------------------------------------------------

In this chapter, we bring a thorough examination of the literature on two topics;
social network analysis together with covert networks, and parameterized complexity.
The study of the former topic provides an useful context for the \HL problem, whereas
the later topic gives us tools to better reason about \NPh problems, among which, as we will see, the \HL problem surely belongs.

%---------------------------------------------------------------
\section{Social network analysis \& covert networks}

First of all, we mention the publication from Morselli \cite{Morselli2009} that the reader can refer to get
an extensive study of criminal networks.
Next, for recent and exhaustive overview of SNA techniques used for covert network disruption,
the reader can use the paper from Ficara et al. \cite{Ficara2022}.

Arguably the most extensive line of research is that in which authors use covert networks to analyze structures consisting of
harmful actors.
That can be terorist organizations or other structures interested in involving into illegal activities. These networks are
also called \emph{dark networks} \cite{Raab2003}.
Indeed, research in this direction have positive impact on understanding such harmful organisations,
shedding light on their inner processes and the most potentially hazardous actors and helping in dismantling the entire network,
preventing further operations and minimizing damage done.
The understanding of how a covert network works inside can lead to understanding of how it can be broken.
Among many others, we mention work of these authors \cite{Waniek2017,Dey2019,Raab2003,Lindelauf2009,Xu2005,Ressler2006, SaavedraNieves2023}.
However, as noted by Saavedra-Nieves and Casas-Méndez \cite{SaavedraNieves2023}, this view on covert networks as organizations with harmful
intends is not the only possible since covert populations can consist for example of drug users, illegal immigrants, persecuted jews,
people with infectious diseases, activists, or ravers \cite{Oliver2014}.
The usefulness of covert network analysis then lingers in analyzing even such populations.
CNA tools, together with other methods of SNA, can be then used even, for example, for analyzing sports teams \cite{Buldú2019}.

The centrality measurement techniques mentioned in the thesis introduction are widely used because
finding the most important vertices within a given network is a natural approach when
studying real-world social networks \cite{Crescenzi2016}.
The most classical centrality measures are degree \cite{Shaw1954}, closeness \cite{Beauchamp1965},
betweenness \cite{Anthonisse1971,Freeman1977}, and core \cite{Seidman1983} centrality.
On top of the standard centrality measures, there are more recent and advanced techniques suitable for measuring one's rank within network,
for example the \emph{Game of Thieves} algorithm from Mocanu et al. \cite{Mocanu2018}, which can be used even within massive networks.
For the sake of completeness, we also mention that there also exist centrality measures on edges, e.g.,
\emph{WERW-Kpath} algorithm from {De Meo} \cite{DeMeo2013}.
The two aforementioned algorithms are more reviewed by Ficara et al. \cite{Ficara2021}.

After detecting influential members within given network using centrality measures,
it is often desirable to talk about their influence in this networks, for which
various \emph{models of influence} can be used.
Among frequently used models belong the \emph{Independent Cascade} model and \emph{Linear Threshold} model.
More on this topic can be found in the book from Easley and Kleinberg \cite{Easley2010}.

Apart from the centrality measures, there are other important tools SNA has to offer.
One of them are \emph{node similarity measures} which are with advantage used in \emph{link prediction} \cite{Zhou2009,Wang2014}.
Link prediction also plays an important part of research of covert networks
as it allows to predict the existence of otherwise hidden connections between members, potentially leading to
identification of important members and relations between them.
This is why covert network users might want to manipulate the network to minimize efficiency of such techniques \cite{Zhou2019}.
Besides CNA, link prediction have other useful applications for example in recommendation systems \cite{Huang2005,Talasu2017}.

Next, we mention that leaders of covert networks often (but not always \cite{Fatih2012}) face what is called
the \emph{efficiency/security trade-off} \cite{Morselli2007} --
the dilemma between staying sufficiently hidden, while keeping enough influence over the network --
which is the often-mentioned topic in the literature about covert networks \cite{Waniek2017,Lindelauf2009,Crossley2012}.
However, the ways in which this trade-off is addressed vary in the literature.
Waniek et al. \cite{Waniek2017}, for example, approach this by modeling the security from the perspective of
centrality measures (centrality measure based secrecy), whereas the efficiency from the perspective of models of influence.
They then show how to construct a network designed specifically to hide its leaders, while
keeping their ability to influence the rest of the network.
Lindelauf et al. \cite{Lindelauf2009}, on the other hand, combine graph and game theory to model this dilemma.

When studying covert networks, we often talk about two parties, the \emph{evaders} and the \emph{seekers};
evaders are members (often leaders) of some covert network;
seekers are then those who try to identify the evaders.
Evaders are typically aware of the importance of their network structure, as can be seen from
the efficiency/security dilemma.
However, when talking about seekers and evaders, authors typically consider these three scenarios:
(i) Evaders act unstrategically in the sense that they are unaware of
the existence of seekers and SNA tools seekers use to reveal them;
(ii) Evaders behave as strategic actors, well-awared of the centrality analysis
seekers use against them \cite{Waniek2017,Dey2019,Waniek2016,Dey2020}.
(iii) Both seekers and evaders are strategic.
To this end, we mention the work from Waniek et al. \cite{Waniek2021} in which the authors propose a strategy
which tells the seekers which centrality measures they should use
to maximize the chances of detecting a leader of a covert network.

In the terminology of this section, the \HL problem describes a covert network consisting of strategic leaders
in the role of evaders, which are trying to evade being detected by the use of centrality measuring techniques,
for which they modify their network by adding new connections between network members.
The leaders do not delete any edges because they face the efficiency/security trade-off and
deleting edges may decrease their efficiency in the network.
The problem is not bound with any influence model and hence can be study independently of it,
leaving the ``efficiency'' part of the efficiency/security trade-off untouched.


%---------------------------------------------------------------
\section{Parameterized computational complexity}

What follows is a sumamry of the literature on the topic of parameterized complexity.
For an introduction to the topic itself, please refer to Section \ref{section:ParamComp}.

The foundations of parameterized complexity were laid by Downey and Fellows
in the series of papers from years 1992 to 1995 \cite{Downey1992,Downey1995.1,Downey1995.2,Downey1993,Downey1995.4},
which the authors further presented later in 1999 in their book \cite{Downey1999},
which was refined and once more published in 2013 \cite{Downey2013}.
Other relevant and potentially useful literature on this topic are
two books by Flum with Grohe \cite{Flum2006} and by Niedermeier \cite{Niedermeier2006} from 2006, book by Hans et al. \cite{Hans2012} from 2012,
book by Cygan et al. \cite{Cygan2015} from 2015 (which to a great extent covers knowledge from the previous literature)
and two books by Haan \cite{Haan2019} and by Fomin et al. (focused mainly on kernelization) \cite{Fomin2019} from 2019.
However, keep in mind that there is a highly active line of research in the field of parameterized complexity, so,
as researchers keep making new discoveries, information presented in the work of mentioned authors may not necessarily be up-to-date.
